### 2024-10-11 draft-2/draft-2.tex
the position after the last move must be valid
added superscripts

@@

\def\subsize{8}%
\font\subrm=\ldfont {\subfamily}{\subsize}{\basefeat}%
\font\subit=\ldifont{\subfamily}{\subsize}{\basefeat}%

@@

\def\sub#1{\lower 0.25ex\hbox{\subrm #1}}%
\def\isub#1{\lower 0.25ex\hbox{\subit #1}}%

@@

\minor A \s{setoption} message is well-formed if it has a prefix
of the form ⟨\ot\s{setoption name} {\it tok}+ \s{value}\ot⟩, where {\it tok}+ is
one or more tokens (none of which are \s{value}) matching an option name listed
in an \s{option} message enqueued by the engine, and a suffix satisfying the
condition(s) for the corresponding option type:

@@

\vskip-0.5\parskip A \s{setoption} message is also well-formed if it is of the
form ⟨\ot\s{setoption name} {\it tok}+\pt⟩ where {\it tok}+ is one or more tokens
(none of which are \s{value}) matching an option name listed in an \s{option}
message enqueued by the engine for which the corresponding option type is
\s{button}.

\minor A \s{position} message is well-formed if it has the form\par
\vskip-\parskip\hskip3ex
⟨\pt\s{position}
  (\ot\s{startpos} \alt\ \s{fen} {\it fen}\ot⁶\pt)
  (\ot\s{moves} {\it mov}+\ot)?\pt\ot⟩\par
\vskip-\parskip where {\it fen}\ot⁶ is an {\caps fen} record and {\it mov}+ is
one or more move tokens. If~\s{fen} is specified, the position described by
{\it fen}\ot⁶ must be valid. If \s{moves} is specified:

@@

\vskip-0.5\parskip Let {\it P}₀ be the starting position if \s{startpos} is
specified and the position described by {\it fen}\ot⁶ if \s{fen} is specified.
Let {\it N} be the number of move tokens specified.

\vskip-0.5\parskip For {\it n} from 0 to {\it N}−1 inclusive, the {\it n}-th
token {\it T}\isub{n} of {\it mov}+ must denote a move {\it M}\isub{n} from
{\it P}\isub{n}. Then let {\it P}\sub{{\subit n}+1} be the position that
immediately follows from {\it P}\isub{n} when {\it M}\isub{n} is applied.

@@

\minor A \s{go} message is well-formed if\ellipsis

>>>>

\def\supfamily{Alegreya Sans Medium}%
\def\supsize{7.4}%
\def\supfeat{:+liga:+clig:+calt:+onum:+pnum}%
\font\suprm=\ldfont {\supfamily}{\supsize}{\supfeat}%
\font\supit=\ldifont{\supfamily}{\supsize}{\supfeat}%
\def\sup#1{\raise 0.73ex\hbox{\suprm #1}}%
\def\isup#1{\raise 0.73ex\hbox{\supit #1}}%

@@

\def\subsize{7.4}%
\def\subfeat{:+liga:+clig:+calt:+onum:+pnum}%
\font\subrm=\ldfont {\subfamily}{\subsize}{\subfeat}%
\font\subit=\ldifont{\subfamily}{\subsize}{\subfeat}%

@@

\def\sub#1{\lower 0.23ex\hbox{\subrm #1}}%
\def\isub#1{\lower 0.23ex\hbox{\subit #1}}%

@@

\minor A \s{setoption} message is well-formed if it has a prefix of the form
⟨\ot\s{setoption name} {\it tok}\ot\sup+ \s{value}\ot⟩, where {\it tok}\ot\sup+
is one or more tokens (none of which are \s{value}) matching an option name
listed in an \s{option} message enqueued by the engine, and a suffix satisfying
the condition(s) for the corresponding option type:

@@

\vskip-0.5\parskip A \s{setoption} message is also well-formed if it is of the
form ⟨\ot\s{setoption name} {\it tok}\ot\sup+\pt⟩ where {\it tok}\ot\sup+ is one
or more tokens (none of which are \s{value}) matching an option name listed in
an \s{option} message enqueued by the engine for which the corresponding option
type is \s{button}.

\minor A \s{position} message is well-formed if it has the form\par
\vskip-\parskip\hskip3ex
⟨\pt\s{position}
  (\ot\s{startpos} \alt\ \s{fen} {\it fen}\ot\sup6\pt)
  (\ot\s{moves} {\it mov}\ot\sup+\ot)?\pt\ot⟩\par
\vskip-\parskip where {\it fen}\ot\sup6 is an {\caps fen} record and
{\it mov}\ot\sup+ is one or more move tokens. If~\s{fen} is specified, the
position described by {\it fen}\ot\sup6 must be valid. Let {\it P}\sub{0} be
the starting position if \s{startpos} is specified and the position described
by {\it fen}\ot\sup6 if \s{fen} is specified. If \s{moves} is specified:

@@

\vskip-0.5\parskip Let {\it N} be the number of move tokens specified.

\vskip-0.5\parskip For {\it n} from 0 to {\it N}−1 inclusive, the {\it n}-th
token {\it T}\isub{n} of {\it mov}\ot\sup+ must denote a move {\it M}\isub{n}
from {\it P}\isub{n}. Then let {\it P}\sub{{\subit n}+1} be the position that
immediately follows from {\it P}\isub{n} when {\it M}\isub{n} is applied.

\vskip-0.5\parskip The position {\it P}\isub{N} must be valid.

@@

\vskip-0.5\parskip The final position (\ot{\it P}\isub{N} if \s{moves} is
specified, otherwise {\it P}\sub{0}\ot) is the position \term{described} by
the \s{position} message.

% TODO state machine: position message “sets” “current position” to P_N

% TODO engine message: bestmove must be valid move from current position

\minor A \s{go} message is well-formed if\pt\ellipsis
